Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-01 paper_comparison/paper_comparison/paper_comparison.Rmd
figures 12 and 13 tweaked a lot

where $B(.)$ is the beta function defined as

@@

```{=tex}
\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda(\beta_0 + \beta_1 log_e(\boldsymbol{E})),
\end{equation}
```
where $\Lambda(.)$ is the standard logistic function given as $\Lambda(z) = exp(z)/(1+exp(z))$.

@@

```{=tex}
\begin{equation} \label{eq:effect-size-ex1}
E = \frac{1}{2\sigma^2}\boldsymbol{X}_b'\boldsymbol{R}_a'(diag(\boldsymbol{R}_a))^{-1}\boldsymbol{R}_a\boldsymbol{X}_b,
\end{equation}
```
where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of $\boldsymbol{R}_a$.

@@

where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vectors of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials, $\varepsilon \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $\{-k, k\}$ defined as

@@

```{=tex}
\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0 + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$.

@@

where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vectors of size $n$ and $g(.)$ is the scaling function defined in \ref{eq:scaling-function}.

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(5, "Safe"))[2:5]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

for (i in target_sigma) {
  j <- j + 1
  plist[[j]] <- 
  VI_MODEL$plot(poly_model(shape = 2, x = rand_uniform())$
                  gen(n = 100, computed = select(mutate(ex_dat, e = sqrt(i) * e), x, e)), theme = theme_light(base_size =  5), 
              remove_axis = TRUE, 
              remove_grid_line = TRUE) +
    ggtitle(round(es[j], 1))
}
```

@@

\begin{landscape}

```{r polypower, fig.height = 3, fig.width = 12, fig.cap="..."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(16, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 15, 11), .))
```

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
    geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(5, "Safe"))[2:5]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

for (i in target_b) {
  j <- j + 1
  plist[[j]] <-
  VI_MODEL$plot(heter_model(a = 1, b = i,x = rand_uniform(-1, 1))$
                  gen(n = 100, computed = select(ex_dat, x, e)), theme = theme_light(base_size =  5),
              remove_axis = TRUE,
              remove_grid_line = TRUE) +
    ggtitle(round(es[j], 1))
}
```

```{r heterpower, fig.height = 3, fig.width = 12, fig.cap="..."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(16, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 15, 11), .))
```

\end{landscape}

>>>>

\noindent where $B(.)$ is the beta function defined as

@@

```{=tex}
\begin{equation} \label{eq:logistic-regression-1-1}
Pr(\text{reject}~H_0|H_1,E) = \Lambda(\beta_0 + \beta_1 log_e(\boldsymbol{E})),
\end{equation}
```
\noindent where $\Lambda(.)$ is the standard logistic function given as $\Lambda(z) = exp(z)/(1+exp(z))$.

@@

```{=tex}
\begin{equation} \label{eq:effect-size-ex1}
E = \frac{1}{2\sigma^2}\boldsymbol{X}_b'\boldsymbol{R}_a'(diag(\boldsymbol{R}_a))^{-1}\boldsymbol{R}_a\boldsymbol{X}_b,
\end{equation}
```
\noindent where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of $\boldsymbol{R}_a$.

@@

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vectors of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials, $\varepsilon \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $\{-k, k\}$ defined as

@@

```{=tex}
\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0 + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
\noindent where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$.

@@

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vectors of size $n$ and $g(.)$ is the scaling function defined in \ref{eq:scaling-function}.

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(5, "Safe"))[2:5]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

for (i in target_sigma) {
  j <- j + 1
  plist[[j]] <- 
  VI_MODEL$plot(poly_model(shape = 2, x = rand_uniform())$
                  gen(n = 100, computed = select(mutate(ex_dat, e = sqrt(i) * e), x, e)), 
                theme = theme_light(base_size =  5), 
              remove_axis = TRUE, 
              remove_grid_line = TRUE, size=0.2) +
    ggtitle(round(es[j], 1)) +
    theme(aspect.ratio=0.8)
}
```

@@

%\begin{landscape}

```{r polypower, fig.height = 3, fig.width = 5, fig.cap="Comparison of power between different tests for nonlinear patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much nonlinearity in the residuals? For the F test (should this be RESET??) this is around log effect size 0.5, but for the visual test it is around 3."}
patchwork::wrap_plots(append(plist, list(p), 
                             after = 0), 
                      design = map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 20, 11), .))
```

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(F_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
    geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.4, linetype = 2) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(5, "Safe"))[2:5]) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

for (i in target_b) {
  j <- j + 1
  plist[[j]] <-
  VI_MODEL$plot(heter_model(a = 1, b = i,x = rand_uniform(-1, 1))$
                  gen(n = 100, computed = select(ex_dat, x, e)), theme = theme_light(base_size =  5),
              remove_axis = TRUE,
              remove_grid_line = TRUE, size=0.2) +
    ggtitle(round(es[j], 1)) +
    theme(aspect.ratio = 0.8)
}
```

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap="..."}
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
                        reduce(c) %>%
                        c(patchwork::area(3, 1, 20, 11), .))
```

%\end{landscape}

### 2022-12-01 paper_comparison/paper_comparison/paper_comparison.tex
figures 12 and 13 tweaked a lot

where \(B(.)\) is the beta function defined as

@@

where \(\Lambda(.)\) is the standard logistic function given as
\(\Lambda(z) = exp(z)/(1+exp(z))\).

@@

where \(diag(.)\) is the diagonal matrix constructed from the diagonal
elements of \(\boldsymbol{R}_a\).

@@

where \(\boldsymbol{y}\), \(\boldsymbol{x}\),
\(\boldsymbol{\varepsilon}\), \(\boldsymbol{x}_{raw}\),
\(\boldsymbol{z}_{raw}\) are vectors of size \(n\), \(He_{j}(.)\) is the
\(j\)th-order probabilist's Hermite polynomials,
\(\varepsilon \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)\), and
\(g(\boldsymbol{x}, k)\) is a scaling function to enforce the support of
the random vector to be \(\{-k, k\}\) defined as

@@

where
\(\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)\).

@@

where \(\boldsymbol{y}\), \(\boldsymbol{x}\),
\(\boldsymbol{\varepsilon}\) are vectors of size \(n\) and \(g(.)\) is
the scaling function defined in \ref{eq:scaling-function}.

@@

\begin{landscape}

@@

\caption{...}\label{fig:polypower}
\end{figure}

@@

\end{landscape}

>>>>

\noindent where \(B(.)\) is the beta function defined as

@@

\noindent where \(\Lambda(.)\) is the standard logistic function given
as \(\Lambda(z) = exp(z)/(1+exp(z))\).

@@

\noindent where \(diag(.)\) is the diagonal matrix constructed from the
diagonal elements of \(\boldsymbol{R}_a\).

@@

\noindent where \(\boldsymbol{y}\), \(\boldsymbol{x}\),
\(\boldsymbol{\varepsilon}\), \(\boldsymbol{x}_{raw}\),
\(\boldsymbol{z}_{raw}\) are vectors of size \(n\), \(He_{j}(.)\) is the
\(j\)th-order probabilist's Hermite polynomials,
\(\varepsilon \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)\), and
\(g(\boldsymbol{x}, k)\) is a scaling function to enforce the support of
the random vector to be \(\{-k, k\}\) defined as

@@

\noindent where
\(\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)\).

@@

\noindent where \(\boldsymbol{y}\), \(\boldsymbol{x}\),
\(\boldsymbol{\varepsilon}\) are vectors of size \(n\) and \(g(.)\) is
the scaling function defined in \ref{eq:scaling-function}.

@@

\%\textbackslash begin\{landscape\}

@@

\caption{Comparison of power between different tests for nonlinear patterns. Main plot shows the power curves, with dots indicating human evaluations of lineups. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much nonlinearity in the residuals? For the F test (should this be RESET??) this is around log effect size 0.5, but for the visual test it is around 3.}\label{fig:polypower}
\end{figure}

@@

\%\textbackslash end\{landscape\}
